Effects of epidemiological structure on the transient evolution of HIV virulence

### 2016-10-11 ms/plos_latex.tex
equation > model

Finally, combining all these equations give us the full model, which is Model 1. We can simply drop the uncoupled and extra-couple transmission terms to obtain equation 2:

@@

Combining all these dynamics, we have equation 3. If we remove extra-couple transmission, we have equation 4.

>>>>

Finally, combining all these equations give us the full model, which is Model 1. We can simply drop the uncoupled and extra-couple transmission terms to obtain model 2:

@@

Combining all these dynamics, we have model 3. If we remove extra-couple transmission, we have model 4.
